Diverse Genotype-by-Weather Interactions in Switchgrass

### 2024-05-09 manuscript/revision2/revision2.qmd
chores: ensure revision2 images render from images folder

![Example hypothesis-driven covariance matrices specified in mash and the posterior weights placed on all covariance matrices. (a) Left column: Five example hypothesized covariance matrices specified for the green-up date or flowering date phenotype; these matrices were created from environment-specific correlations across eight common gardens, and are described in Table XXX. Common gardens are arranged in latitudinal order within the matrices. Right column: Five example canonical covariance matrices. Canonical matrices (purple) have simple interpretations, such as equal effects across all common gardens, or effects specific to a single common garden. (b,d) Total posterior weight placed on each covariance matrix type specified for (b) green-up date and (d) flowering date mash models, within and between two genetic subpopulations. Hypothesized covariance matrices (green). Covariance matrices included in mash that had zero posterior weight in all three mash runs on the genetic subpopulations, such as the identity matrix, are not shown. (c,e) Total posterior weight placed on covariance matrices that were hypothesized or canonical, for the (c) green-up date phenotype and (e) flowering date phenotype.](Figure_2_recolor_covariance_matrices_and_posterior_weights.png){#fig-covar}

![Types of GxE present between of pairs of jointly re-estimated effects in eight common gardens, for effects with lfsr \< 0.05. a) Examples of effect patterns at three pairs of sites with three types of GxE. Sign: Effects that differ in sign at these pairs of gardens (p \< 0.05, lfsr). Magnitude: Effects identical in sign (p \< 0.05, lfsr) that differ in magnitude by a factor of \>0.4. None: Effects not distinguishable by magnitude nor sign of the effect. b) The fraction of effects with each GxE type for the start of vegetative growth (Greenup Date) and reproductive growth (Flowering Date), within and between two genetic subpopulations. Common gardens are grouped by the larger region they came from: North gardens are within the natural range of the Midwest subpopulation, while Texas gardens are within the natural range of the Gulf subpopulation.](Figure_3_GxE.png){#fig-effects}

![Overlaps of QTL from an outbred pseudo-F2 cross and with jointly re-estimated SNP effects in the 1% tail of significance from a diversity panel. Dotted lines indicate permutation-based significance thresholds for each weather-related function. Stars indicate QTL with significant enrichment for SNPs in the 1% mash tail; G, M, and B indicate which subpopulation had enrichment: G - Gulf subpopulation, M -Midwest subpopulation, B - both subpopulations. Rug plots show genomic locations of SNPs in the 1% mash tail for flowering date for each subpopulation. a) QTL mapping for the start of vegetative growth (Greenup Date), and three weather-related functions of greenup date. b) QTL mapping for the start of reproductive growth (Flowering Date), and two weather-related functions of flowering date.](Figure_4_QTL_Overlaps.png){#fig-qtl}

>>>>

![Example hypothesis-driven covariance matrices specified in mash and the posterior weights placed on all covariance matrices. (a) Left column: Five example hypothesized covariance matrices specified for the green-up date or flowering date phenotype; these matrices were created from environment-specific correlations across eight common gardens, and are described in Table XXX. Common gardens are arranged in latitudinal order within the matrices. Right column: Five example canonical covariance matrices. Canonical matrices (purple) have simple interpretations, such as equal effects across all common gardens, or effects specific to a single common garden. (b,d) Total posterior weight placed on each covariance matrix type specified for (b) green-up date and (d) flowering date mash models, within and between two genetic subpopulations. Hypothesized covariance matrices (green). Covariance matrices included in mash that had zero posterior weight in all three mash runs on the genetic subpopulations, such as the identity matrix, are not shown. (c,e) Total posterior weight placed on covariance matrices that were hypothesized or canonical, for the (c) green-up date phenotype and (e) flowering date phenotype.](images/Figure_2_recolor_covariance_matrices_and_posterior_weights.png){#fig-covar}

![Types of GxE present between of pairs of jointly re-estimated effects in eight common gardens, for effects with lfsr \< 0.05. a) Examples of effect patterns at three pairs of sites with three types of GxE. Sign: Effects that differ in sign at these pairs of gardens (p \< 0.05, lfsr). Magnitude: Effects identical in sign (p \< 0.05, lfsr) that differ in magnitude by a factor of \>0.4. None: Effects not distinguishable by magnitude nor sign of the effect. b) The fraction of effects with each GxE type for the start of vegetative growth (Greenup Date) and reproductive growth (Flowering Date), within and between two genetic subpopulations. Common gardens are grouped by the larger region they came from: North gardens are within the natural range of the Midwest subpopulation, while Texas gardens are within the natural range of the Gulf subpopulation.](images/Figure_3_GxE.png){#fig-effects}

![Overlaps of QTL from an outbred pseudo-F2 cross and with jointly re-estimated SNP effects in the 1% tail of significance from a diversity panel. Dotted lines indicate permutation-based significance thresholds for each weather-related function. Stars indicate QTL with significant enrichment for SNPs in the 1% mash tail; G, M, and B indicate which subpopulation had enrichment: G - Gulf subpopulation, M -Midwest subpopulation, B - both subpopulations. Rug plots show genomic locations of SNPs in the 1% mash tail for flowering date for each subpopulation. a) QTL mapping for the start of vegetative growth (Greenup Date), and three weather-related functions of greenup date. b) QTL mapping for the start of reproductive growth (Flowering Date), and two weather-related functions of flowering date.](images/Figure_4_QTL_Overlaps.png){#fig-qtl}
